% !TEX root = main.tex

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

Several institutions have given me their support. First of all, I would like to thank the \textbf{Van Gogh Museu}m for the administrative and financial support provided through their sponsoring agreements with \textbf{AXA Research Fund} and \textbf{ASML}, without which this research would have not been possible. I am grateful to the \textbf{University of Amsterdam} for accepting my application as a PhD student as well to the \textbf{Rijksdienst voor het Cultureel Erfgoed} for the technical and practical support. I am also indebted to the \textbf{Rijksmuseum} and \textbf{NICAS} working space I was able to occupy during the PhD.\\ 


My first words of thanks go to \textbf{Frank Ligterink}, since none of this would have happened without his initial support. Frank has supported me since the beginning of my professional career, and through him I obtained the financial and administrative support of the Van Gogh Museum to carry out this thesis. \\

I had wonderful supervisors: \textbf{Ella Hendriks}, \textbf{Klaas Jan van den Berg}, and \textbf{Rob Erdmann}. It has been a pleasure to work under your guidance and I am proud to say that I obtained my doctoral status under your supervision. Your trust and your support were the main factors contributing to the successful completion of this thesis. \textbf{Ella}, thank you for your numerous comments regarding the writing of this dissertation. \textbf{Klaas Jan}, I appreciated very much for your thoughtfulness and your ongoing support regarding the usefulness of the stereo-MFT. \textbf{Rob}, I enjoyed and learnt so much during our regular meetings. Your advice and help contributed to a large extent to the success of this research. \\

I also wish to thank the members of my defence committee for taking the time to read and review my dissertation. \\
 
Many people have helped with specific tasks all along the PhD, fro which I thank them. First, I wish to express my gratitude to my colleagues from the Paper conservation studio of the Rijksmuseum (\textbf{Idelette van Leeuwen, Dyonisa Christoforou, and Martin Jürgens}) for letting me use the photographic room and the luxmeter. I am also grateful to my colleagues from the Metal conservation studio of the Rijksmuseum (\textbf{Sarah Creange} and \textbf{Tamar Davidowitz}) for helping me with the threads of the 3D printed objects. I am also indebted to \textbf{Susan Smelt}, from the Painting conservation studio of the Rijksmuseum, for giving me access to the Mavospec spectrometer; these measurements have played a central role in some of my experiments. I am aslo grateful to \textbf{Dan Giesen} from the technical department of the University of Amsterdam who has helped me to create the 3D prints required for the stereo-MFT. I would also like to acknowledge my colleagues at the Van Gogh Museum (\textbf{Kees van den Meiracker}, \textbf{Ana Martin}, \textbf{Domenico Casillo}, \textbf{Saskia van Oudheusden}, and \textbf{Anneke van Stralen}). Kees, thank you for your supervision and for connecting me with other projects from the Van Gogh Museum. \textbf{Ana}, I appreciated your support and your interest in my work, I hope that we will have a chance to collaborate. \textbf{Domenico}, thank you for taking the time to discuss the lighting conditions in the galleries of the museum and for letting me use LED lamps from the Van Gogh Museum. These lamps have been extremely useful! \textbf{Saskia}, thank you for finding the time to help me access the \textit{Sunflowers} reconstruction painting. I appreciated having the possibility to perform colour measurements and microfading analyses on this object. \textbf{Anneke}, thank you for helping access my Van Gogh Museum account at the end of my contract. I appreciated your kindness and your help. Several colleagues from the \gls{RCE} have helped all along the PhD (\textbf{Agnes Brokerhof}, \textbf{Muriel Geldof}, \textbf{Han Neevel}, \textbf{Art Proa\~{n}o Gaibor}, \textbf{Suzan de Groot}, \textbf{Bauke Zeilstra}). Thank you \textbf{Agnes}, for your advice regarding light-ageing experiments and lighting policies, I enjoyed the light management workshop you gave at Het Nieuwe Instituut in Rotterdam. Thank you \textbf{Muriel} for showing me how to use the Zeiss microscope and for sharing your knowledge on Van Gogh's artists' materials. Thank you \textbf{Han} for the many discussions and advice about light-induced colour change phenomena. Thank you \textbf{Art} for taking the time to make the chrome yellow paint with me. I extensively used these paints in my experiments. \textbf{Suzan}, I appreciated the time you took to perform FTIR analyses on the eosin pigments made by Alba. \textbf{Bauke}, thank you for your support and for giving me the opportunity to work at the \gls{RCE}. It really helped me to finish the PhD under such favourable conditions.  I received help to make two pigments for which I am grateful, since many of my experiments are based on paint-outs made with these two pigments. Firstly, \textbf{Vanessa Otero} from the NOVA university in Lisbon, has been extremely kind and generous with her time in helping me make chrome yellow pigment. Secondly, \textbf{Alba Alvarez-Martin} and \textbf{Teresa Scovacricchi} from the \gls{UA} kindly agreed to make eosin pigment for me. I would also like to thank \textbf{Kirsten Dunne}, \textbf{Christel Pesme}, \textbf{Stefan R\"{o}hrs}, and \textbf{Carlos Morales-Merino} for their comments and help concerning microfading-related questions that I had. \\

My office mates are not to be forgotten - \textbf{Rika Pause, Alessandra Marrocchesi, Sanne Berbers, and Elsemieke van Rietschoten}. Beyond walls and naughtiness flows a river of friendship that always refreshes us. Thank you for the fun time we had and will have together.\\

J'ai la chance d'avoir un groupe d'amis exceptionel (\textbf{Olivier, Lilas, Maxence, Riko, Nicolas, Yassine, Anaïs, Etienne, Gab, Maxime, Mathieu, Andres}), même si l'on ne se voit pas souvent, votre amitié m'a toujours été précieuse et déterminante dans la plupart des moments importants de ma vie. Je souhaite aussi remercier ma famille au sens large, mais aussi mes parents plus particulièrement. La concrétisation de ces cinq années de travail est aussi la réussite de toute une vie parentale. \\

Finally, my last thoughts go to my partner \textbf{Tracy}. I am grateful for the time you took to thoroughly edit parts of my dissertation, but I am even more grateful to have you in my life!